Between Subgraph Isomorphism and Maximum Common Subgraph

### 2017-01-31 poster/poster.tex
applications block, better key, graph font and space fixes

Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
handle problem instances with many hundreds of vertices in the pattern graph, and up to \textbf{ten thousand
vertices} in the target graph, leading to successful application in areas such as \textbf{computer
vision}, \textbf{malware detection}, \textbf{compilers}, \textbf{model checking}, \textbf{biochemistry}, and \textbf{pattern recognition}.
}

\vspace*{3cm}

\block{Maximum Common Subgraph (Comparing Graphs)}{
\begin{wrapfigure}[11]{r}{0.46\linewidth}
    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Na) at (0,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nb) at (0, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nc) at (2, 0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nd) at (2, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (Ne) at (1, -4) 
        {\vphantom{0}};

@@

   \end{tikzpicture}\end{center}

    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
         \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N1) at (0,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N2) at (0,  -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N3) at (2, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N4) at (4, 0) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N5) at (4, -4) {\vphantom{0}};

@@

\block{$k$-less Subgraph Isomorphism (Finding Most of a Pattern)}{

>>>>

\block{Applications}{
Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
handle problem instances with many hundreds of vertices in the pattern graph, and up to \textbf{ten thousand
vertices} in the target graph, leading to successful application in areas such as \textbf{computer
vision}, \textbf{malware detection}, \textbf{compilers}, \textbf{model checking}, \textbf{biochemistry}, and \textbf{pattern recognition}.
}
%\vspace*{3cm}

\block{Maximum Common Subgraph (Comparing Graphs)}{
\begin{wrapfigure}[6]{r}{0.46\linewidth}
    \begin{center}\begin{tikzpicture}[scale=1.1]%{{{
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Na) at (0,  0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nb) at (0, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nc) at (2, 0)
        {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (Nd) at (2, -2)
        {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (Ne) at (1, -4) 
        {\vphantom{0}};

@@

        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N1) at (4,  0) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N2) at (4,  -4) {\vphantom{0}};
        \node[draw, circle, fill=white, inner sep=5pt, font=\bfseries] (N3) at (6, -2) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N4) at (8, 0) {\vphantom{0}};
        \node[draw, circle, fill=uofgcobalt, inner sep=5pt, font=\bfseries] (N5) at (8, -4) {\vphantom{0}};

@@

\block{$k$-less Subgraph Isomorphism (Most of a Pattern)}{
